\Huge Conferences in the Era of Expensive Carbon

### 2019-06-04 main.tex
More work

A possible short-term response to both questions involves {\em carbon
  offsets}---a tool by which organizations (and individuals) can voluntarily
impose a price on their own emissions.
%
% What they are:
In a nutshell, the idea is that a conference can raise funds from
registration fees or corporate sponsors and give them, via a carbon offset
{\em vendor}, to a {\em provider} who will use them to support an activity
(e.g., installing methane capture devices on landfill sites or buying
efficient cookstoves to replace open-fire cooking in developing areas) that
avoids emitting an amount of greenhouse gases equivalent to the emissions
from participants' travel to the conference.
%
\begin{itemize}
\item Lots of organizations (universities, companies) are already doing
this; some ACM conferences are starting to experiment with voluntary carbon
offset fees at registration time.
\end{itemize}

\begin{itemize}
\item There are also some significant
concerns.
\item Concern: Organizations are not set up to do it, and the piecemeal
political and bureaucratic work of designing and implementing a separate
policy for each organization is exhausting.
\item Concern: It is hard to choose the price (right now there is an
oversupply), and setting it too low leads to complacency --- it doesn't
really bite, so it doesn't change people's behavior.  The current market
price of carbon is still quite low (around \$15 per ton), whereas the
``social cost of carbon'' is variously estimated at anywhere from \$40 to
\$400 per ton~\bcp{citation}.
Experts agree that the current price will need to rise significantly
over time to achieve the required effect.
\item This issue leads many people to argue that offsets "let people off the
hook" and encourage inaction, but we believe it is consistent with
encouraging action -- especially if offsets are priced right, but even if
(in the short term) they are too cheap -- because it injects a ``price
signal'' that makes emissions something for planners to optimize.
\item We feel that, on balance, voluntary carbon offsets are an effective
tools for raising awareness and changing organizational behavior in the
short term.
\item Moreover, supporting well-chosen carbon mitigation activities has a
clear benefit and can be done now.
\end{itemize}

>>>>

A possible short-term response to both questions involves {\em carbon
  offsets}---a tool by which organizations (and individuals) can voluntarily
impose a price on their own emissions.
%
% What they are:
In a nutshell, the idea is that a conference can raise funds from
registration fees or corporate sponsors and give them, via a carbon offset
{\em vendor}, to a {\em provider} who will use them to support an activity
(e.g., installing methane capture devices on landfill sites or buying
efficient cookstoves to replace open-fire cooking in developing areas) that
avoids emitting an amount of greenhouse gases equivalent to the emissions
from participants' travel to the conference.
%
Many organizations (including numerous universities, companies such as
Google, Dell, Microsoft, General Motors, Delta Airlines, Expedia, and
others) are already buying carbon offsets; some ACM conferences have already
started to experiment with voluntary carbon offset fees at registration
time.

We acknowledge that there are some significant concerns with carbon offsets.
\begin{itemize}
\item Concern: Organizations are not set up to do it, and the piecemeal
political and bureaucratic work of designing and implementing a separate
policy for each organization is exhausting.
\item Concern: It is hard to choose the price (right now there is an
oversupply), and setting it too low leads to complacency --- it doesn't
really bite, so it doesn't change people's behavior.  The current market
price of carbon is still quite low (around \$15 per ton), whereas the
``social cost of carbon'' is variously estimated at anywhere from \$40 to
\$400 per ton~\bcp{citation}.
Experts agree that the current price will need to rise significantly
over time to achieve the required effect.
\item This issue leads many people to argue that offsets "let people off the
hook" and encourage inaction, but we believe it is consistent with
encouraging action -- especially if offsets are priced right, but even if
(in the short term) they are too cheap -- because it injects a ``price
signal'' that makes emissions something for planners to optimize.
\item We feel that, on balance, voluntary carbon offsets are an effective
tools for raising awareness and changing organizational behavior in the
short term.
\item Moreover, supporting well-chosen carbon mitigation activities has a
clear benefit and can be done now.
\end{itemize}
